---
title: |
  | Indoor Air Quality & DIY HEPA Filter 
  | Seattle Airpocalypse
date: '22-23 August 2018'
output:
  bookdown::pdf_document2:
    number_sections: no
    toc: no
geometry: margin = 0.75in
fontsize: 10pt
link-citations: true
linkcolor: blue
urlcolor: blue
---

```{r knitr.global.options, include=F}
knitr::opts_chunk$set(echo=F, 
                      warning=F, 
                      fig.align='center', 
                      fig.pos='H',
                      fig.width=12, 
                      fig.height=8, 
                      fig.path='Figs/', 
                      tidy.opts=list(width.cutoff=60),
                      tidy=TRUE)
options(scipen=999)
```

```{r load.packages, include=F}
# Load pacman, installing as necessary.
my_repo <- 'http://cran.r-project.org'
if (!require("pacman")) {install.packages("pacman", repos = my_repo)}

# Load the other packages, installing as needed.
pacman::p_load(knitr, bookdown, dplyr, kableExtra)
```

```{r upload.and.clean.data, include=F, eval=F}
 ## Read in datasets for 2012-2016 county level estimates from USGS website https://water.usgs.gov/nawqa/pnsp/usage/maps/county-level/

airdata <- read.delim('estimates/EPest.county.estimates.2012.txt', header=T)

```

# Summary

Wildfires in California, Oregon, Washington, and British Columbia resulted in several poor air quality days in the summers of 2017 and 2018. Previously, the term ["airpocalypse" has been used in the headlines](https://abcnews.go.com/International/460-million-chinese-residents-suffering-airpocalypse/story?id=44329107) to describe smog events around the world. In August 2018, the Seattle Times ran a number of articles on the topic:

* [Aug 15, 2018: Smoke to clear up from Seattle skies but threatens return next week](https://www.seattletimes.com/seattle-news/weather/smoke-to-clear-up-from-seattle-skies-but-threatens-return-next-week/)
* [Aug 16, 2018: As smoke hangs over Northwest study shows air pollution was already high](https://www.seattletimes.com/seattle-news/environment/as-smoke-hangs-over-northwest-study-shows-air-pollution-was-already-high/)
* [Aug 19, 2018: Smoky air returns to Seattle through at least Wednesday](https://www.seattletimes.com/seattle-news/environment/smoky-air-returns-to-seattle-through-at-least-wednesday/)
* [Aug 20, 2018: Washington's smoky air looks scary but UW physician says trust your body's defenses](https://www.seattletimes.com/seattle-news/health/washingtons-smoky-air-looks-scary-but-uw-physician-says-trust-your-bodys-defenses/)
* [Aug 22, 2018: Seattle weather on verge of major shift back to normal](https://www.seattletimes.com/seattle-news/weather/seattle-weather-on-verge-of-major-shift-back-to-normal/)
* [Aug 25, 2018: Changing winds bring smoke back to Seattle could stay through Sunday](https://www.seattletimes.com/seattle-news/changing-winds-bring-smoke-back-to-seattle-could-stay-through-sunday/)
* [Aug 27, 2018: Yes, we can do something about the wildfire smoke](https://www.seattletimes.com/opinion/yes-we-can-do-something-about-the-wildfire-smoke/). 

The [Puget Sound Clean Air Agency](https://www.pscleanair.org/35/About-Us) provides valuable data to protect public health, improve neighborhood air quality, and reduce the region’s contribution to climate change. According to their monitors (nephalometer), the highest particulat

This report shares my family's findings from an at-home experiment that utilized real-time particle counting with a ([Dylos Air Quality Monitor](http://www.dylosproducts.com/learnabout.html) to evaluate the impact of a [do-it-yourself (DIY) high-efficiency particulate air (HEPA) filter](https://www.king5.com/article/news/local/this-diy-air-filter-for-wildfire-smoke-is-less-than-20/281-584346009) described by the Puget Sound Clean Air Agency.


-----

